\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Tài liệu tham khảo}

\bibitem{vaswani2017}
A. Vaswani, N. Shazeer, N. Parmar, J. Uszkoreit, L. Jones, A. N. Gomez, L. Kaiser, and I. Polosukhin, ``Attention Is All You Need,'' in \textit{Advances in Neural Information Processing Systems (NeurIPS)}, vol. 30, 2017, pp. 5998--6008.

\bibitem{gemini2024}
Google DeepMind, ``Gemini: A Family of Highly Capable Multimodal Models,'' \textit{arXiv preprint arXiv:2312.11805}, 2024.

\bibitem{smith2015}
R. Smith, ``An Overview of the Tesseract OCR Engine,'' in \textit{Proc. 9th Int. Conf. Document Analysis and Recognition (ICDAR)}, vol. 2, 2007, pp. 629--633.

\bibitem{flutter2024}
Google, ``Flutter: Beautiful native apps in record time,'' \textit{Flutter Documentation}, 2024. [Online]. Available: \url{https://flutter.dev/docs}. [Accessed: 15-May-2026].

\bibitem{nodejs2024}
OpenJS Foundation, ``Node.js Documentation,'' 2024. [Online]. Available: \url{https://nodejs.org/en/docs}. [Accessed: 15-May-2026].

\bibitem{postgresql2024}
The PostgreSQL Global Development Group, ``PostgreSQL 16 Documentation,'' 2024. [Online]. Available: \url{https://www.postgresql.org/docs/16/index.html}. [Accessed: 15-May-2026].

\bibitem{lusardi2019}
A. Lusardi and O. S. Mitchell, ``The Economic Importance of Financial Literacy: Theory and Evidence,'' \textit{Journal of Economic Literature}, vol. 52, no. 1, pp. 5--44, 2014.

\bibitem{thaler2009}
R. H. Thaler and C. R. Sunstein, \textit{Nudge: Improving Decisions About Health, Wealth, and Happiness}. New York, NY, USA: Penguin Books, 2009.

\bibitem{chen2021}
S. Chen, M. Mao, and Y. Sun, ``A Review of Personal Finance Management Applications Based on Artificial Intelligence,'' in \textit{Proc. IEEE Int. Conf. on Artificial Intelligence and Computer Applications (ICAICA)}, 2021, pp. 458--463.

\bibitem{auer2022}
R. Auer, J. Frost, L. Gambacorta, C. Monnet, T. Rice, and H. S. Shin, ``Central bank digital currencies: motives, economic implications, and the research frontier,'' \textit{Annual Review of Economics}, vol. 14, pp. 697--721, 2022.

\bibitem{jwt2015}
M. Jones, J. Bradley, and N. Sakimura, ``JSON Web Token (JWT),'' \textit{Internet Engineering Task Force (IETF), RFC 7519}, May 2015. [Online]. Available: \url{https://tools.ietf.org/html/rfc7519}.

\bibitem{fielding2000}
R. T. Fielding, ``Architectural Styles and the Design of Network-based Software Architectures,'' Ph.D. dissertation, University of California, Irvine, 2000.

\end{thebibliography}
